### 2013-08-27 thesis/src/chapters/chapter-1.tex
Add business subsection to the motivation

>>>>

\subsection{Business}
The rapid growth of interest in cloud computing in recent years resulted in huge sums of money being invested in the field. Figure \ref{ch1:public-cloud-services-market-size} shows the size of the public cloud services market in 2012 and the forecast of its nearly two times growth in 2016. This data suggests that the subject is attractive for IT industry from the economic point of view. However, higher amounts of money spent on cloud services involves higher expectation of theirs quality.

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-1/public-cloud-services-market-size}
  \end{center}
  \caption{Public Cloud Services Market Size, 2010-2016 (forecast)}
  \label{ch1:public-cloud-services-market-size}
\end{figure}
